\chapter{Introduction}
\label{introduction}
 
\subsection*{Motivation}

Because the quantum mechanics  is now 'old' and established theory, there has been a push towards applying the quantum mechanics to the more and more complex systems. In addition, there  has been a push to apply quantum mechanical principles to processes where physics intersects with other disciplines.

Two of those disciplines are an Information Theory and material science.

Within Information Theory framework, promising route to quantum information processing \cite{QIP} is via the manipulation of the internal states of ions and atoms. Within the new materials framework, there is a great stride in creating new 2D materials, with great promises. \cite{Nature2D}
In order to facilitate that emergent technology it is imperative that we understand, at a fundamental level, the processes that govern the behavior of matter at the atomic level. In this thesis we will explore the interactions of ions with neutral matter. Those topics include radiative quenching, non-radiative and radiative charge transfer reactions as well as the manipulation and control of atomic matter by external fields.

The quantitative calculations have greatly been helped with the advancement in computing technology, since it is now possible to solve the differential equation relatively quickly and using computing equipment which is widely accessible.  However applying only approximative methods and using only numerical methods to solve differential equations may not be sufficient in number of cases. While the numerical methods will always provide a result, they do not provide much of an insight into the behavior of a quantum system. Also, unless one is very careful, the various numerical errors tend to accumulate, and it that case the result is neither insightful nor correct. So the analytic solution is almost always desirable. Although for the moderately complex system the closed form analytic solution is usually impossible to obtain, it is still desirable to have the exact analytic solution and fall back to the approximations and numerical methods only as a last step.

The statement above is generally true and applicable to every project and solution. So in this problem we tried to find the analytical solution and fall back on the numerical computation only as a last step. So while the Quantum Mechanics can be applied to any physical system, relative to this thesis we see two major applications: new 2 dimensional materials and quantum computing.

\subsection*{New Materials}

Applying quantum mechanics to more complex systems brought us electronics componenta, lasers, high speed telecommunications, new diagnostic technologies in medicine, new materials, and in general, new applications are being researched.

After it discovery, at the beginning of this century, the quantum mechanics have been applied to more and more complex system. One of its application has been understanding the properties of materials.
From the understaning of the properties of the materials, came the icreation of the new materials, using the quantum mechanical principles. And 2D materials were investigated fairly early in the 2th century.
Initially, it was argued by Landau and Peierls \cite{LandauG}\cite{Pierls} that 2D materials cannot exist. The argument was that the displacement of atoms due to the thermal fluctuations would be an order or the atomic distance, at any finite temperature \cite{LandauG, Pierls}. Thus 2D material would melt at any temperature higher that $ 0 K $. Therefore the only 2D materials considered were a molecular films, which would form on the surface of solids. From Dash \cite{2DMatter1}, the 2D materials exist as a thin film either on surface on the boundaries of the 3D materials.

The other kind research in 2 dimensional systems was motivated by the need to simplify the theoretical investigations. Often, simpler 1 or 2 dimensional  conceptual models are used to analyze the physical phenomena. From that simpler model, a 3 dimensional model is than treated as the same, just more mathematically complex system.  following those arguments, the application of  quantum mechanics in 2 dimension was initially done as an analysis of the surface phenomena. \cite{2dfilm}. 

However, despite those arguments, it has been speculated that 2D materials are possible \cite{2DMatter1}. The situation has changed dramatically in 2004 when it turns out that 2D materials can indeed exist \cite{Graphene0}. The first 2D material, graphene was created \cite{GrapheneN} at the university of Manchester.

The 2D materials have qualitatively different topological properties \cite{2DMatterCurvature}. Moreover, these properties do not depend on the type of microscopic interactions between particles. While this subject is beyond the scope of this thesis, it does show that the field of 2D materials has excellent potential for both fundamental research and applications. For the material to exhibit 3D properties, it has been shown \cite{GraphLayers} that when material has as low as 10 layers, its properties are approaching the 3D limit.

Interestingly, following \cite{Graphene0} it seems that 2D materials have another set of interesting properties, in the regions where particles in 2D behave relativistically. Usually, in condensed mater system, the ordinary Schroedinger equation is sufficient to describe all the electronic properties of the material. In Graphene, the electrons themselves still behave non-relativistically. But there interaction with the periodic potential of the graphene lattice gives rise to new quasi-particles, known as the massless Dirac's fermions. These quasi-particles, even at low energies, can only be described by the Dirac's equation in 2+1 dimensions. Therefore it might be interesting to redo the same calculation as we did, but solving the Dirac's equation for the system of quasi-particles similar to an Hydrogen ion.  There are many other interesting properties of Graphene \cite{Graphene0}, such as its QED like electronic spectrum, electron tunneling, and so on. The other interesting consequence of the QED like electron spectrum is the possibility of experimentally studying QED in curved space, by controllable bending of a graphene sheet. This can offer a possibility to address a certain class of cosmological problems. 

Now, after the discovery of Graphene, there has been an extensive study regarding the new 2D materials. and the research has really picked up. Now there are number of new 2D materials being discovered.  The main application in in the direction nanotubes and of 2D semiconductors. While nanotubes are made of graphene, they are not equivalent and depending on the application Graphene (as a sheet) is sometimes superior, sometimes inferior and sometimes completely different.

As far as the electronics, the hope that the Graphene can be used to build active electronic components, such as diodes, transistors (FET) and such. Alternatively due to its conductivity, Graphene can be used as a conductor, in both electronic components but also in the batteries. Graphene itself is a zero gap semiconductor. The unique opportunity in 2D semiconductors is that in 3D semiconductor electronic states are not buried deep inside the material. In 2D semiconductors, the electronic states are on the surface. The more interesting application of 2D electronics are the LED elements in 2D \cite{2DLED}. The research in electronics is closely related to the research of new 2D materials. For example Graphene itself is not compatible with Silicon. But there is a new material, Black Phosphorus, which is both compatible with Silicon and it posses a band gap, which also makes it able to detect light. TODO: more here

\subsubsection*{2D Electronics}

One application of the 2D materials is their use in electronic devices \cite{2DEJour}. This is driven by the demand for the higher performance and lower consumption in electronic devices.

\subsection*{Topological Quantum Computing}

Applying quantum mechanical principles in engineering disciplines, such as computer science \cite{FQC} promises to bring us the much qualitatively more powerful quantum computer. This computer may possibly able to solve problems currently intractable by classical digital computers. Currently it is not clear whether the quantum computer will be able to solve NP problems. TODO: (Add citation). Now all problems in the NP class can be transformed into each other in polynomial time to each other TODO add citation,  therefore finding a polynomial time solution for one of them would amount to having a polynomial time solution to the all problems in NP class. So the goal is rather worthy.

Currently, there are not final word on the subject yet. While most authors lean to the opinion that the quantum computer may not be fundamentally more powerful than the classical one, there are schemes \cite{NLQC} which would allow quantum computer to solve NP problems. As an related example the Schor's algorithm \cite{Schor} can provaly solve integer factorization in a polynomial time, as opposed to the best classical algorithm (quadratic sieve), which works in sub-exponential time \cite{Pomerance}. Unfortunately, the integer factorization problem does not belong to the class of NP problems. 

Even if the NP problems remain intractable, just the possibility that, according to Feynman \cite{FQC}, quantum computer can be used to simulate the quantum processes,will in itself be a step forward in modeling the physical properties and processes. In addition quantum computers may offer some other benefits in terms of space, energy consumptions. TODO" add citation.

What relates the new 2D materials and the quantum computing architecture, is the concept of topological quantum computing \cite{Tqc1}.  While, in principle, there are no theoretical objections to building a quantum computer, there are serious issues encountered in practice TODO: add citations. Currently these problems are not solved and the quantum computers currently in existence are still unable to overcome them TODO: add citations.
It seems that the topological approach promises an actually physically realizable quantum computer \cite{Tqc2,Tqc3}. And 


\subsection*{Anyons}

Anyons are the quasiparticles which occur only in 2D systems and whose quantum statistics in neither Fermionic nor Bosonic \cite{Anyons1}.  This has been proved  \cite{Anyons2}, and the arbitrary statistics is valid only in 2 dimensions \cite{Walsh}. After exchanging two identical particles, the wave function gains an arbitrary phase factor $ \Psi = e^{i\theta}\Psi $, where $ \theta = 2\pi\nu^{s} $. This is in contrast the 3 dimensional world, where exchange of two particles gains either phase factor $ \pi $ or $ 0 $, for Fermions and Bosons respectively.

There are two kinds of Anyons, Abelian and non-Abelian. The Abelian anyons have been reliably detected in the Fractional Quantum Hall Effect. \cite{FQHE}.  While the computation with Abelian anyones is theoretically possible \cite{AbelianAnyons}, considerably more attention has been paid to the non-Abelian anyons.
There are several possibilities for realizing non-abelian statistics experimentally: 1. a two-dimensional electron gas in a large magnetic field (the fractional quantum Hall effect); 2. rapidly rotating Bose-Einstein condensates 3. frustrated magnets.

Non-abelian anyons have not been detected yet, but most of the research have been focused on them as  they could offer some interesting applications, most notably  fault tolerant Topological Quantum Computing. \cite{AnyonsTqc}. But since the Anyons are only observed in 2D topologies, one must start from the 2D materials.


\subsection{Excitons and Trions}

The other interesting and relatively simple system is the Exciton, which represents a bound state of a whole and a electron in a solid state material, and allows the transport of energy without transport of an electric charge. There are two types of Excitons: 

1. Frenkel exciton which is found in organic molecular crystals \cite{Excitons3} with binding energy of $ 1eV $ and radius of $ ~ 10\text{\AA} $ and 
2. Wannier exciton, found in in semiconductors \cite{Excitons2}  with binding energy of $ ~1meV $ and radius of $ ~100\text{\AA} $

Exciton have been observed in 2D materials \cite{Excitons2D1, Excitons2D2} and also as 2D Excitons in 3D materials. The promise here is that these kind of quasiparticles can help create a new kind of electronic components, typically opto-electronics.

Since the exciton system resembles the Hydrogen molecule, and it seems conceivable that the dynamics of  $ H2^{+} $ molecule is qualitatively similar and could be applied to the excitons systems as well.

The similar system is a Trion, which consists of either 2 electrons and a hole, or 2 holes and an electron, therefore resembling the hydrogen molecule.

\subsubsection{Future Applications and Speculations}

While the applications of the 2D materials above are certainly interesting, creating an exact analytical  model of such material is extremely complex. Even with todays computing machinery, the wave equations for many bodies quantum system are unsolvable, even numerically.  Equations for many bodies systems may formally be created by extending equations for a one or two bodies systems. But as soon as one tries that, one realizes that the complexity of such equations increases enormously, and than assumptions  made for a small systems are not valid any more. In this author's opinion, moving from a simple system to an order of magnitude more complex, requires a completely new mathematical and physical framework. Something analogous between the classical mechanics and thermodynamics.

\subsubsection{Outline}

While all the applications of the 2D materials above are certainly interesting and promising, it is doubtful that there is going to be an exact analytical model of the above systems. So, we turn our attention to the Hydrogen atom and molecule, which have provided, throughout history of physics, a starting point which we can analyze and use the results to predict the behavior of the more complex systems. 

In this thesis we will focus on solving the simplest molecular system, namely Hydrogen Molecular Ion $ {H_2^{+}}  $ in 2 dimensions (2D in the further text), and solving such system in 2D exactly.  In chapter 1 we will show that applying our method to the already solved and well known $ {H_2^{+}} $ in 3D yields the same results. Then in chapter 2 we will follow  the already well established procedure \cite{Bates1} to analytically solve the $ {H_2^{+}} $. After providing an analytical solution, we will fall back to the numerical methods, in order to calculate the energy levels, and the potential curves,. In chapter 3 we use the results obtained to calculate the dynamics of such system, namely the Radiate Association process. In chapter 4 we again use the same results to calculate the Radiate Charge Transfer. 

All this brings us to the next chapter, where we re-calculate the electron energies for Hydrogen Molecular Ion in 3D, by using different and arguably simpler approach.
